Welcome to the Center! I am really excited for the professional journey that lies ahead for you. The Center has been a key part of my own collegiate career. It's not just a job -- I feel that I have grown a lot as a writer, student, citizen, community member, and all the other hats that I wear as a student here. My main piece of advice to you would be this: keep an open mind about the opportunities you have to for personal growth through engagement with the Center. Although appointments are the backbone of the your work at the Center, they are just part of the picture.

That said -- I think especially as a mathematics tutor -- you may find yourself sitting next to a student at some point wondering ``Why am I here trying to hint to this student that $4x + 7x$ can be simplified to $13x$? What is the point?'' The point is not about the math problem. It's not even really about the math concept. Really, the point of your appointment work at the Center is to help students feel supported in their coursework -- that there is a safety net under the tightrope -- and a valued part of the campus community. While some of the mathematical ideas you might discuss with students are invigorating (especially the first semester or two on the job), the real magic dust is your personal relationship with the students. This is what makes the appointment transaction valuable to you and, although they might not consciously appreciate it, the student. Students want to know about you. What's it like doing the job? How did you decide to be a math major? Do you get paid when nobody shows up for appointments? (Apparently, this last one is a common concern among clients). Show the same interest and engagement and you'll be well on your way to sharing and enjoying for yourself magic dust of the Center. I really am going to miss working at the Center after I graduate but, like other aspects of campus life I feel very closely connected to, it makes me happy to know that students like you will carry the work forward. Please do not hesitate to get in touch at any point during your time at the Center and beyond.

Again, congratulations on being invited to join the Center. A lot of good things are in store for you.